Scalar and Representative Models for Polarimetric SAR Data

### 2013-05-18 paper_dev/article_pp.tex
201305_May18 update from last version of 201305_May17

The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
  before making inferences about the inherent ENL.
The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
  it is possible to estimate the ``effective'' number of look, by finding an $L$ that ensures the above relationship is valid.
This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.

In this section, an alternative approach making use of variance statistics in the homoskedastic log-domain to find ENL is proposed.
Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
\begin{equation}
  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
  \label{eqn:expected_sample_var_log_as_function_of_enl}
\end{equation}
where $\psi^1()$ again denotes the tri-gamma function.

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[ENL and variance log-intensity relations for SAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
		 \label{plot_enl_var_relation_1x1}
	} 
	\hfill	
	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
		 \label{plot_enl_var_relation_2x2}
	} 
\end{tabular}
\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots}
\label{fig:plot_enl_var_relation_1x1_and_2x2}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[ENL and variance log-intensity relations for SAR data]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
		 \label{plot_enl_var_relation_1x1}
	} 
	\hfill	
	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
		 \label{plot_enl_var_relation_2x2}
	} 
\end{tabular}
\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
\label{fig:plot_enl_var_relation_1x1_and_2x2}
\end{figure}
%endif

@@

To demonstrate the improvement obtained using this ENL estimation,  a sample  single-look complex fine-quad RADARSAT2 dataset is used. 
A nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
  against the theoretical models for the nominal ENL value of 9.
As expected the match is evidently not very close.

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics. However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL and model the data reasonably well.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics. Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}
%endif

The same approach can be applied on the AIRSAR Flevoland data to improve the validational match described earlier.
Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
\label{fig:handling_airsar_oversampling_practice_full_pol}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
\label{fig:handling_airsar_oversampling_practice_full_pol}
\end{figure}
%endif

@@

The model is far from complete.
 It reduces the multi-dimensional POLSAR data to a scalar value.
While this is probably desirable for a wide range of application,
  such a reduction is unlikely to be lossless.
Thus to better understand POLSAR data
  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g. the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).

However the proposed model is also promising.
Eventhough initially developed for partial and monostatic POLSAR data,
  it was later shown to be applicable to traditional SAR data as well.
Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.

@@

Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, 
new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.

@@

Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
In fact better results can be achived.
In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not very well suited for digital image presentation,
  which is linear and additive in nature.
Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.

To evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
  and the two POLSAR speckle filters are then applied to the patch.
\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.

@@

Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
  the distortion impact of the filter can also be made visible by the residual image.
In visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
in the additive log-determinant image of the filtered output, 
  such an observation can be made relatively easier by inspecting the residual image.

There are many similar SAR data processing technique that may be adaptable to POLSAR.
Examples in the same topic of evaluating speckle filters include
  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.

@@

A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
  resulting in several consistent discrimination measures for POLSAR applications.
The theoretical models are shown to be powerful in that:
  not only it can provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
They are also practically useful since they lead to several consistent discrimination measures.
Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.

@@

This completes the first phase of the derivation process.
The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
  and converting natural logarithm into base-2 logarithm.
First, setting $L=1$ makes the above results become
\begin{eqnarray*}
   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
\end{eqnarray*}
with $\gamma$ denoting the Euler-Mascharoni constant.
Then to convert to base-2 logarithm from natural logarithmic transformation,
  we again use the variable change theorem.
  That is:
  \begin{eqnarray*}
   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
  \end{eqnarray*}
\begin{eqnarray*}
   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
\end{eqnarray*}
\begin{eqnarray*}
  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{eqnarray*}

>>>>

The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
  before making inferences about the inherent ENL.
The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
  it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.

We will instead propose an alternative approach making use of variance statistics in the homoskedastic log-domain.
Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
\begin{equation}
  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
  \label{eqn:expected_sample_var_log_as_function_of_enl}
\end{equation}
where $\psi^1()$ again denotes the tri-gamma function.

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[ENL and variance log-intensity relations for SAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
		 \label{plot_enl_var_relation_1x1}
	} 
	\hfill	
	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
		 \label{plot_enl_var_relation_2x2}
	} 
\end{tabular}
\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots.}
\label{fig:plot_enl_var_relation_1x1_and_2x2}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[ENL and variance log-intensity relations for SAR data]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
		 \label{plot_enl_var_relation_1x1}
	} 
	\hfill	
	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
		 \label{plot_enl_var_relation_2x2}
	} 
\end{tabular}
\caption{The relation between ENL and sample variance of log-determinant/log-intensity.}
\label{fig:plot_enl_var_relation_1x1_and_2x2}
\end{figure}
%endif

@@

To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
  against the theoretical models for the nominal ENL value of 9.
As expected the match is evidently not very close.

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics. However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL which matches the data much more closely.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics. Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}
%endif

The same approach can be applied on the AIRSAR Flevoland data to improve the validation described earlier.
Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
  even though it is to a much lesser extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through to a lesser extent than the RADARSAT2 data.}
\label{fig:handling_airsar_oversampling_practice_full_pol}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
\label{fig:handling_airsar_oversampling_practice_full_pol}
\end{figure}
%endif

@@

The model is far from complete.
 It reduces the multi-dimensional POLSAR data to a scalar value.
While this is probably desirable for a wide range of application,
  such a reduction is unlikely to be lossless.
Thus %to better understand POLSAR data
the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g. the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar).

However the proposed model is promising.
Even though initially developed for partial and monostatic POLSAR data,
  it was shown to be applicable to traditional SAR data as well.
Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.

@@

Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, 
new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
%***IVM remove this single sentence, it detracts from the argument...
%Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.

@@

Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
In fact better results can be achieved.
In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
  which is linear and additive in nature.
Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.

To briefly evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
  and the two POLSAR speckle filters are then applied to the patch.
\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.

@@

Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
  the distortion impact of the filter can also be made visible by the residual image.
In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
in the additive log-determinant image of the filtered output, 
  such an observation can be made relatively easier by inspecting the residual image.

Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
Evidently these techniques can also be adapted for POLSAR.
Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.

Hai version: (Ian have not seen this yet) There are many similar SAR data processing technique that may be adaptable to POLSAR.
Examples in the same topic of evaluating speckle filters include
  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.

@@

A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
  resulting in several consistent discrimination measures for POLSAR applications.
The theoretical models are shown to be powerful in that
  not only can they provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
  but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
They are also practically useful since they lead to several consistent discrimination measures.
Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.

@@

This completes the first phase of the derivation process.
The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
  and converting natural logarithm into base-2 logarithm.
First, setting $L=1$ makes the above results become:
\begin{eqnarray*}
   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
\end{eqnarray*}
with $\gamma$ denoting the Euler-Mascharoni constant.
Then to convert to base-2 logarithm from natural logarithmic transformation,
  we again use the variable change theorem.
  That is:
  \begin{eqnarray*}
   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
  \end{eqnarray*}
\begin{eqnarray*}
   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
\end{eqnarray*}
\begin{eqnarray*}
  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{eqnarray*}
